\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-22 paper/mswp2012-proposal.tex
Fixing some typos and notes from the tutor

Recent studies show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercisement, especially in the so called western society. Many studies and health reports in Europe and America describe the problem and show an increasing trend towards being overweight. The biggest problem being the situation getting worse and worse - especially children are rapidly becoming a big part of the problem, the risk of being overweight is about 30 percent\footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. \\

Studies\citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays. Being overweight not only affects your attractiveness, it can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.  \\

@@

One reason for the negative trend of childhood overweight are bad role models. Parents living an unhealthy lifestyle affect and influence their children. A recent study suggests that at-risk children are identifyable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. With increased age it gets harder to get in shape, the goal should be to teach children at young ages how to become and stay fit. In the future this negative trend will lead to an increased financial claim in our health care system - more and more people need expensive health treatments because of diseases caused by being obese over the years.  \\

>>>>

Recent studies show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercise, especially in the so called western society. Many studies and health reports in Europe and America describe the problem and show an increasing trend towards being overweight. The biggest problem in this area is that the situation is getting worse and worse. Especially children are rapidly becoming a big part of the problem, the risk of being an overweight child is about 30 percent, according to the Center for Disease Control \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. \\

Studies\citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays. Being overweight affects your life in a lot of ways. From today's point of view overweight people are less attractive than others, have less success and and are more likely to be the victims of day-to-day discrimination \ref{carr05}. Moreover obesity can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.  \\

@@

One reason for the negative trend of childhood overweight are bad role models. Parents living an unhealthy lifestyle affect and influence their children. A recent study suggests that at-risk children are identifiable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. With increased age it gets harder to get in shape, the goal should be to teach children at young ages how to become and stay fit. In the future this negative trend will lead to an increased financial claim in our health care system - more and more people need expensive health treatments because of diseases caused by being obese over the years.  \\
